MultiDataImportPico

### 2023-12-06 Code/MultiDataImportPico.Rmd
Changes to read_csv

@@

unzip(DataIn, list = TRUE)

#check file names

@@

TargetFile <- unzip(DataIn, "20211223_PICO_MCMIX006_RUN42.csv")

TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")

TargetFileName

@@

```{r fread_plus}
fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
}
```

@@

```{r Read TargetFile}
#abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
#abs-time not currently used?
# TargetData <- fread_plus(Flnm = TargetFile, Skip = "key") %>%
# select(-c(V5))

#run this if V5 is the 'value' column
TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
   select(-c(V5))

# %>%
#  select(-c(value)) %>%
#   rename(value = V5)

TargetData[1:10,]

#check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
unique(TargetData$key)
```

@@

TargetData <- TargetData %>%
  select(key, time, `abs-time`, value, Filename, CDateTime) %>%
  mutate(Tube = str_extract(key, "-[:digit:]"),
         Tube = as.numeric(str_extract(Tube, "[:digit:]")),
         abs_time = dmy_hms(`abs-time`)) %>%
  select(-`abs-time`)

>>>>

Skip <- 19

@@

#List files in the extracted folder with a ".asc" extension
# MCFiles <- unzip(DataIn, list = TRUE)
# MCFiles <- MCFiles[grepl(".csv$", MCFiles$Name), "Name"]
# print(MCFiles)

@@

TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"

# This opens a compressed file without decompressing.
TargetData <- read_csv(unz(DataIn, TargetFile),  skip = 20, id = "path", col_names = c("key", "time", "abs-time", "value")) %>% 
  separate(col = path, into = c("path", "Filename"), sep = ":")

# TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")
# 
# TargetFileName

@@

```{r fread_plus}
# fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
#     mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
# }
```

@@

```{r Read TargetFile}
# #abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
# #abs-time not currently used?
# # TargetData <- fread_plus(Flnm = TargetFile, Skip = "key") %>%
# # select(-c(V5))
# 
# #run this if V5 is the 'value' column
# TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
#    select(-c(V5))
# TargetData <- fread_plus(Flnm = paste(DataIn, "20211223_PICO_MCMIX006_RUN42.csv", sep = ":"), Skip = "key")  %>%
#    select(-c(V5))
# # %>%
# #  select(-c(value)) %>%
# #   rename(value = V5)
# 
# 
# TargetData[1:10,]
# 
# #check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
# unique(TargetData$key)
```

@@

TargetData <- TargetData %>%
  select(key, time, `abs-time`, value, Filename) %>% #, CDateTime
  mutate(Tube = str_extract(key, "-[:digit:]"),
         Tube = as.numeric(str_extract(Tube, "[:digit:]")),
         abs_time = dmy_hms(`abs-time`)) %>%
  select(-`abs-time`)
